\documentclass[11pt, aspectratio=169]{beamer}
% ==========================================
% Theme & Color Settings (Moloch Theme)
% ==========================================
\usetheme{moloch}
\usecolortheme{moloch}
% ==========================================
% Modular Preambles & Configurations (Relative)
% ==========================================
\input{../../preamble/packages.tex}
\input{../../preamble/macros.tex}
\input{../../preamble/listings-setup.tex}
% ==========================================
% Presentation Metadata
% ==========================================
\title{FedMAQ: Communication-Efficient Federated Learning via Multi-Adaptive Quantization and Knowledge Distillation}
\subtitle{BS/MS Computer Science Thesis Update}
\author{Christian Joseph Bunyi}
\institute{Dr. Andrew L. Tan Data Science Institute \\ De La Salle University}
\date{\today}
% ==========================================
% Slide Deck Document Structure
% ==========================================
\begin{document}

% Slide 1: Title Slide
\begin{frame}[plain]
    \titlepage
\end{frame}

% ==========================================
% Section 1: The FedMAQ Architecture
% ==========================================
\begin{frame}{The FedMAQ Architecture}
    We propose a hybrid codesign addressing both system and statistical heterogeneity:
    \vspace{0.3cm}
    \begin{itemize}
        \item \textbf{Client-Side Compression:} Clients dynamically compress payload bit-widths using multi-adaptive quantization based on memory constraints, dataset sizes, and gradient norms. We draw inspiration from the doubly-adaptive scaling principles in (Hönig et al., 2022).
              \vspace{0.2cm}
        \item \textbf{Server-Side Aggregation:} To mitigate quantization noise and non-IID client drift, the server aggregates client logits via proxy-based knowledge distillation. This isolates the computational distillation burden entirely to the server, as demonstrated in (He et al., 2025).
    \end{itemize}
\end{frame}

% ==========================================
% Section 3: The 3-Dimensional Quantization
% ==========================================
\begin{frame}{FedMAQ's Multi-Adaptive Quantization}
    \small
    FedMAQ dynamically adjusts each client's transmission bit-width based on three dimensions of awareness:
    \vspace{0.2cm}
    \begin{itemize}
        \item[] \textbf{1. Resource Awareness (Memory Constraint):} \\
              Acts as a hard ceiling. It limits the maximum allowable bit-width to prevent Out-of-Memory (OOM) failures on resource-constrained edge devices (He et al., 2025).
        \item[] \textbf{2. Data Awareness (Dataset Size):} \\
              Clients with larger local datasets possess more representative statistical distributions. FedMAQ allocates higher precision to these clients to preserve their updates (Hönig et al., 2022).
        \item[] \textbf{3. State Awareness (Gradient Norm):} \\
              Adapts to the local optimization state. High gradient norms indicate large model updates, while low norms suggest proximity to a local minimum (Cui et al., 2026; Liu et al., 2023).
    \end{itemize}
\end{frame}

% ==========================================
% Section 4: Baseline Taxonomy
% ==========================================
\begin{frame}{Baselines}
    \centering
    \vspace{0.2cm}
    \begin{table}
        \fontsize{8pt}{10pt}\selectfont
        \begin{tabular}{l l p{6.5cm}}
            \toprule
            \textbf{Category}          & \textbf{Algorithms} & \textbf{Architectural Note}                                                                                                    \\
            \midrule
            \textbf{Seminal Controls}  & FedAvg, FedProx     & Standard parameter-averaging without compression.                                                                              \\
            \midrule
            \textbf{Pure Quantization} & FedPAQ, DAdaQuant   & Uplink compression without function-space error mitigation.                                                                    \\
            \midrule
            \textbf{Pure Distillation} & FedMD, FEDDISTILL+  & Sharing logits/soft-labels to mitigate non-IID drift. We benchmark against the FEDDISTILL+ configuration (Jeong et al., 2018). \\
            \midrule
            \textbf{Hybrid Q+KD}       & FedKD, CFD          & Combines compression and distillation.                                                                                         \\
            \midrule
            \textbf{Proposed}          & \textbf{FedMAQ}     & \textbf{Combines multi-adaptive quantization with server-side distillation.}                                                   \\
            \bottomrule
        \end{tabular}
    \end{table}
    \vfill
    {\fontsize{8pt}{9.5pt}\selectfont *Note: Algorithms with no public implementations (DynFed, FedDT) were explicitly excluded.}
\end{frame}

% ==========================================
% Section 5: Manuscript Progress
% ==========================================
\begin{frame}{Manuscript Progress}
    \begin{center}
        \textbf{\textcolor{blue}{[Cue: Switch to the manuscript]}}
    \end{center}
\end{frame}

% ==========================================
% Section 6: Next Steps
% ==========================================
\begin{frame}{Next Steps}
    \begin{itemize}
        \item Review and optimize existing baseline algorithms replications.
        \item Refine theoretical framework and methodology chapter narratives.
    \end{itemize}
\end{frame}

% Slide 7: Q&A
\begin{frame}[standout]
    Thank You!
    \vspace{0.5cm}
    \begin{center}
        \large Questions \& Answers
    \end{center}
\end{frame}

\end{document}
